Computation and comparison of the stable Northeastern US marine boundary layer

### 2020-12-05 Paper/results.tex
More nomenclature stuff
updated computation performance

%%%%%%%%%%%%%%% Compare Nalu/AMR integrated quantities %%%%%%%%%%%%%%
\begin{table}
\caption{\label{tab:CompareAMRvsNalu} Comparison of AMR-Wind and
  Nalu-Wind} \centering
\begin{tabular}{cccccc}
  \hline
  Code & Wind speed & TI      &  $\alpha$  &   $u_\tau$ \\ %&       L \\
  \hline
  Nalu-Wind & 5 m/s &  0.0481 &  0.165     &  0.163 m/s \\ %& 94.970836 \\
  AMR-Wind  & 5 m/s &  0.0483 &  0.166     &  0.157 m/s \\ %& 52.512434 \\
  \hline
\end{tabular}
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

For the 5 m/s SBL case AMR-Wind had a median time of 0.266 seconds per time step.
This means the entire simulation took about 6 hours to simulate 20k seconds
of physical time. For this case a total of $288\times 288 \times 384$ cells were used
which were solved in parallel using 972 MPI ranks. Simulations were carried out using NREL's
Eagle supercomputer and AMR-Wind was compiled using Intel 2018.
Typically on CPU's we see a strong scaling limit at around 15k cells per MPI rank.
But for this case we used 32,768 cells per MPI rank which is about half the strong scaling limit.
The time per degree of freedom for AMR-Wind is
\[\frac{n_r t_{ts} }{n_{dofs}} = 8\times10^{-6} [s]\]
where $n_r$ is the number of MPI ranks, $t_{ts}$ is time per time step, and $n_{dofs}$ is
the total number of degrees of freedom (for AMR-Wind we are using the number of cells).
This value allows us to compare speed relative to Nalu-Wind when using a different
grid and number of MPI ranks, where a smaller value means a faster time to solution.

In comparison, the same case for Nalu-Wind takes 3.404363 seconds per time step which
takes a total of 75.65 hours to complete the simulation. This simulation was carried out
on 1224 MPI ranks on a grid that contains $300\times 300 \times 400$ cells. The equivalent
time per degree of freedom for Nalu-Wind is $1.032 \times 10^{-4}$ s.

>>>>

%%%%%%%%%%%%%%% Compare Nalu/AMR integrated quantities %%%%%%%%%%%%%%
\begin{table}
\caption{\label{tab:CompareAMRvsNalu} Comparison of AMR-Wind and
  Nalu-Wind ABL statistics} \centering
\begin{tabular}{cccccc}
  \hline
  Code & Wind speed & TI      &  $\alpha$  &   $u_\tau$ \\ %&       L \\
  \hline
  Nalu-Wind & 5 m/s &  0.0481 &  0.165     &  0.163 m/s \\ %& 94.970836 \\
  AMR-Wind  & 5 m/s &  0.0483 &  0.166     &  0.157 m/s \\ %& 52.512434 \\
  \hline
\end{tabular}
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

For the 5 m/s SBL case AMR-Wind had a median time of 0.266 seconds per time step.
This means the entire simulation took about 6 hours to simulate 20k seconds
of physical time. For this case a total of $288\times 288 \times 384$ cells were used
which were solved in parallel using 972 MPI ranks. Simulations were carried out using NREL's
Eagle supercomputer and AMR-Wind was compiled using Intel 2018.
Typically on CPU's we see a strong scaling limit at around 15k cells per MPI rank.
But for this case we used 32,768 cells per MPI rank which is about half the strong scaling limit.
The time per degree of freedom for AMR-Wind is
\[\frac{n_r t_{ts} }{n_{dofs}} = 8.118\times10^{-6} [s]\]
where $n_r$ is the number of MPI ranks, $t_{ts}$ is time per time step, and $n_{dofs}$ is
the total number of degrees of freedom (for AMR-Wind degrees of freedom are taken to be
 number of cells in the grid). This value allows us to compare speed relative to 
Nalu-Wind when using a different grid and number of MPI ranks, where a smaller value 
means a faster time to solution. It should be noted that the choice to use fewer 
elements for AMR-Wind was to ensure perfect load balancing across MPI ranks. This 
$288 \times 288 \times 384$ grid can be perfectly decomposed into smaller $32^3$ blocks.

In comparison, the same case for Nalu-Wind takes 3.404 seconds per time step which
takes a total of 75.64 hours to complete the simulation. This simulation was carried out
on 1224 MPI ranks for a grid that contains $300\times 300 \times 400$ cells. The equivalent
time per degree of freedom for Nalu-Wind is $1.147 \times 10^{-4}$ s, where degrees of freedom
are the number of nodes in the mesh.

For both AMR-Wind and Nalu-Wind each time step is dominated by the linear solver work. 
A time step within AMR-Wind requires two poisson solves (MAC and nodal projection),
a tensor Helmholtz solve for Momentum equations, and two scalar Helmholtz solves 
(potential temperature equation and subgrid-scale kinetic energy equation).
Nalu-Wind is a fully implicit scheme and requires a non-linear Picard iteration for each time
step, in this work we use two Picard iterations for every time step.
Each Picard iteration requires a Poisson solve and five Helmholtz solves
(three momentum equations, an Enthalpy equation, and the subgrid-scale kinetic energy equation).
It is difficult to compare AMR-Wind and Nalu-Wind due to the differences in discretization and numerical
implementation. The most significant difference between the two solvers is that AMR-Wind uses structured grids
whereas Nalu-Wind uses unstructured grids. There is a lot of computational overhead with storing
and manipulating unstructured data.
